IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/abstract.tex
jcmnew intro

\begin{abstract}
    Many important security problems in JavaScript, including extension
    security~\tocite{}, inclusion of untrusted libraries~\tocite{} and
    mash-up security~\tocite{}, could be solved with a implementation
    of information flow control.  However, designing an IFC system which
    can be \emph{efficiently} implemented is quite a challenge.  In this paper,
    we formally describe a coarse-grained IFC system which fulfills this
    criterion.  The key idea is that an efficient IFC system must not
    depend too much on the details of the language it is integrated
    with.  The result is a \emph{general} method for adding IFC to existing
    languages which is \emph{indifferent} to the choice of language.
    Additionally, we describe how to relate concrete implementations
    with the IFC systems produced by our technique and show how various
    proposed and existing IFC systems fit into our formal framework.
\end{abstract}

>>>>

\begin{abstract}
Many important security problems in JavaScript, such as browser extension
security, untrusted JavaScript libraries and
safe integration of mutually distrustful websites (mash-ups), 
may be effectively addressed using an efficient implementation
of course-grained information flow control.
Using JavaScript as a motivating and illustrative example, 
we formally specify a coarse-grained IFC system that
can be implemented non-intrusively in a variety of language contexts, 
resulting in
much greater implementation efficiency than previous finer-grained approaches.
The main advance involves identifying isolation mechanisms
that allow IFC to track interaction between program
components whose internal operation is not tracked
because the entire component has the same label.
By presenting other language examples, we suggest that this 
is a general method for adding IFC to existing
languages,
provided an appropriate isolation mechanism can be identified.
We also describe how to relate optimized concrete implementations
to the IFC systems produced by our technique.
\end{abstract}

### 2014-07-08 paper/intro.tex
Fix low-level nits found by reviewers.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
jcmnew intro

Modern web content is rendered using a potentially large number of
different components with differing provenance.
Disparate and untrusting components may arise from browser
extensions (whose JavaScript code runs alongside website
code), web applications (with possibly untrusted third-party
libraries), and mashups (which combine code and data from
websites that may not even be aware of each other's existence.)
While just-in-time combination of untrusting components
offers great flexibility, it also poses complex security challenges.
In particular, maintaining data privacy in the face of malicious
extensions, libraries, and mashup components has been difficult,
and in general effectively impossible.

Information flow control (IFC) is a promising technique
that provides security
by tracking the flow of sensitive data through a system.
Untrusted code is confined so that it cannot exfiltrate data, except as
per an information flow policy.  Significant research has been devoted to
adding various forms of IFC to different kinds of programming languages
and systems.  In the context of the web, however, there is a strong
motivation to preserve the language JavaScript, and retrofit dynamic information
flow control on top of it.  A key challenge in dynamic information
flow control is implementation efficiency: when
information flow is tracked at a fine-grained level,
e.g., per value in the system, systems may incur
impractical runtime overhead~\cite{JSFlow}.
%
Moreover, the task of adding fine-grained IFC even to a simple language is
non-trivial~\cite{hritcu2013testing}; when considering a real-world language,
such as JavaScript, this challenge becomes almost insurmountable.

In the alternative \textit{coarse-grained} approach to IFC,
a system is divided into relatively coarse computational units,
each with a single label dictating its security policy.
Only
communication between isolated computational units must be tracked.
A recent system named SWAPI~\cite{swapi} adds IFC to the
browser by identifying \emph{web workers} as an existing computational
unit.  Communication between workers is mediated using
IFC to ensure non-interference, preventing sensitive workers from
influencing the computation of less sensitive workers.
This coarse-grained approach provides a number of advantages:
(1) reduced runtime overhead because checks need only
be performed at isolation boundaries, (2) minimal changes to an
existing programming language when adding IFC, which (3) allows
the reuse of existing programs.  Finally, (4) associating
a single security label with the entire computational unit simplifies
understanding and reasoning about the correctness of the
system, without information flow reasoning about the
technical details of the semantics of the programming language.

A further benefit of the coarse-grained approach
is that a single IFC design and semantics can be generalized
to a large class of programming languages.
Leveraging this insight, we define a general form of coarse-grained
dynamic IFC and show how it can be combined with \emph{any} programming
language conforming to a general semantic framework.
At the core of our IFC system is a sandboxing construct that isolates
potentially sensitive computations, allowing them to
communicate only through clearly specified interfaces.
Using the Matthews-Findler approach~\cite{Matthews:2007:OSM:1190216.1190220}
for combining operational semantics,
we formally state and prove non-interference guarantees that are
independent of the choice of specific target language.

One challenge in the design of our system is that the semantics for the
retrofitted IFC language may not accurately correspond to the optimized
implementation details of a particular target language.
We discuss and partially address this issue
by characterizing isomorphisms between the operational semantics of our
defined language and a concrete implementation, showing that if this
relationship holds, then non-interference in the abstract specification
carries over to the concrete specification.

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  information flow control language.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Section~\ref{sec:retrofit})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism, and show a class of restrictions on
  the IFC language that preserves non-interference. (Section~\ref{sec:formal})
  \item We connect our formal semantics to real implementations of
  coarse-grained IFC systems for JavaScript and Haskell, and explain
  how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
  \item We briefly describe ways to enrich the core IFC language with
  more advanced concepts such as labeled values, privileges, or a
  notion of clearance. (Section~\ref{sec:extensions})
  \item We informally relate our results to a monadic interpretation
      of IFC which guided our design. (Section~\ref{sec:monad})     
\end{itemize}

@@

>>>>

The way modern web content is rendered, using a potentially large number of
different components with differing provenance, illustrates the need for 
general methods to track data provenance and use in complex software systems.
Disparate and untrusting software components may arise from browser
extensions whose JavaScript code runs alongside website
code, web applications with possibly untrusted third-party
libraries, and mashups which combine code and data from
websites that may not even be aware of each other's existence.
While just-in-time combination of untrusting components
offers great flexibility, it also poses complex security challenges.
In particular, maintaining data privacy in the face of malicious
extensions, libraries, and mashup components has been difficult,
with no previous comprehensive principled solution.

Information flow control (IFC) is a promising technique
that provides confidentiality (and integrity, as desired)
by tracking the flow of sensitive data through a system.
Untrusted code is confined so that it cannot exfiltrate data, except as
permitted by an explicit information flow policy.  
Significant research has been devoted to
adding various forms of IFC to different kinds of programming languages
and systems.  In the context of the web, however, there is a strong
motivation to preserve the language, JavaScript, and retrofit dynamic information
flow control on top of it.  
However, adding fine-grained IFC even to a simple language is
non-trivial~\cite{hritcu2013testing} and 
tracking fine-grained information flow for each
value in the system may incur
impractical runtime overhead~\cite{JSFlow}.

In an alternative \textit{coarse-grained} approach to IFC we advance 
in this paper, a system is divided into relatively coarse computational units,
each with a single label dictating its security policy.
It is only necessary to track
communication between isolated computational units.
A recent system named SWAPI~\cite{swapi} adds IFC to the
browser by identifying \emph{web workers} as an existing computational
unit.  Communication between workers is mediated using
IFC to ensure non-interference, preventing sensitive workers from
influencing the computation of less sensitive workers.
This coarse-grained approach provides a number of advantages:
(1) reduced runtime overhead because checks need only
be performed at isolation boundaries, (2) minimal changes to an
existing programming language when adding IFC, which (3) allows
the reuse of existing programs.  Finally, (4) associating
a single security label with the entire computational unit simplifies
understanding and reasoning about the correctness of the
system, without information flow reasoning about the
technical details of the semantics of the programming language.

We show how a coarse-grained approach suggested by
SWAPI can be applied generally to the JavaScript language and 
similarly generalized to a large class of programming languages
that provide a suitable isolation mechanism.
At the core of our coarse-grained IFC system is a sandboxing construct that isolates
potentially sensitive computations, allowing them to
communicate only through clearly specified interfaces.
Using the Matthews-Findler approach~\cite{Matthews:2007:OSM:1190216.1190220}
for combining operational semantics,
we formally state and prove non-interference guarantees that are
independent of the choice of specific target language.
While the semantics for the
retrofitted IFC language may not accurately correspond to the optimized
implementation details of a particular target language, 
we discuss and partially address this issue
by characterizing isomorphisms that imply non-interference for the concrete specification.

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  information flow control language.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Section~\ref{sec:retrofit})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism, and show a class of restrictions on
  the IFC language that preserves non-interference. (Section~\ref{sec:formal})
  \item We connect our formal semantics to real implementations of
  coarse-grained IFC systems for JavaScript and Haskell, and explain
  how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
  \item We briefly describe ways to enrich the core IFC language with
  more advanced concepts such as labeled values, privileges, or a
  notion of clearance. (Section~\ref{sec:extensions})
\end{itemize}

The systems we have implemented allow and appropriately track
external effects. For example, SWAPI treats XMLHttpRequest by
wrapping the ``native'' unsafe code. 
However, general treatment of external effects difficult and
current information flow control systems suffer limitations.
For instance, JPMail [A] re-implements primitives with external effects in Jif; 
Paragon [B] internalizes external effects by wrapping the corresponding primitives
to be IFC-aware [C]; JSFlow [25,26] manually wraps JavaScript primitives with external effects.

@@

\cut{DM had some very good comments on how to make this sound less
  like a pitch for LIO. Outline for something more compelling (not
  necessarily in this order):
\begin{itemize}
  \item Motivate IFC
  \item Coarse grained IFC is easy
  \item Coarse grained IFC is sufficient (vs. fine grained); do by citation
  \item We have the right API and it's language-agnostic; proof is also language independent
  \item You can ``drop it in''
\end{itemize}
}
